\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Fixed Graphs
Small corrections
Some coding and small changes to tex

	\if1\blind
	{
		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
		\author{Anastasios Panagiotelis\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			Puwasala Gamakumara\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: George.Athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Rob.Hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

@@

	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.  Since by definition, $\bm{s}_j$ lies in in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.  Stacking these vectors horizontally
	\begin{align}
	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
	\bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
	\end{pmatrix}\\
	&=\begin{pmatrix}
	\bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
	\end{pmatrix}\\
	&=\bm{S}
	\end{align}

>>>>

	\if1\blind
	{
		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
		\author{Anastasios Panagiotelis\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			Puwasala Gamakumara\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: George.Athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Rob.Hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

\begin{figure}[!h]
    \centering
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
        \caption{\small}
    \end{subfigure}
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
        \caption{\small}
    \end{subfigure}
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
        \caption{\small}
    \end{subfigure}
     \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
        \caption{\small}
    \end{subfigure}
    \caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection_new}
\end{figure}

@@

	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.  Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.  Stacking these vectors horizontally
	\begin{align}
	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
	\bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
	\end{pmatrix}\\
	&=\begin{pmatrix}
	\bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
	\end{pmatrix}\\
	&=\bm{S}
	\end{align}
